Replication in Archaeological Science: Shape as a Measure of Weapon Standardisation

### 2020-02-23 analysis/paper.Rmd
Corrected missing use of here() in ggsave and commented out the ggsave line of code due to errors

---
title: "Replication analysis"
author: "Team Fresh"
date: "2/12/2020"
output: html_document
---

@@

#install_version("geomorph", version = "3.0.6", repos = "http://cran.us.r-project.org")
library(geomorph) # geomorph 3.0.6

#install_version("shapes", version = "1.2.3", repos = "http://cran.us.r-project.org")
library(shapes) # shapes 1.2.3

@@

# The results are significant, but they cannot be explained by site difference
lances_ANOVA<-procD.allometry(shape ~ size, ~site, data=lances_geomorph,method="PredLine") # Optional right-hand formula for the inclusion of groups; "~site" can be removed to perform ANOVA on whole dataset

# lances_ANOVA<-procD.allometry(shape ~ size, data=lances_geomorph,method="PredLine") # As above, but with "~site" removed
plot(lances_ANOVA)
print(lances_ANOVA)

@@

# plot the grid
ggpairs(lances_M, columns = c("total_length", "blade_length", "socket_length", "sock_bdiam", "sock_sdiam", "width", "thickness"), 
        upper=list(continuous = "points", mapping = aes(color = site)),
        lower=list(continuous = "cor"),
        ggsave("Images/replication_fig_8v1.png"))

@@

ggpairs(lances_M, columns = c("total_length", "blade_length", "socket_length", "socket_max", "socket_min", "width", "thickness"), 
        upper=list(continuous = "points", mapping = aes(color = site)),
        lower=list(continuous = "cor"),
        ggsave("Images/replication_fig_8v2.png"))

>>>>

---
title: "Replication in Archaeological Science: Shape as a Measure of Weapon Standardisation"
author: "Team Fresh"
date: "2/24/2020"
output: html_document
---

@@

#install_version("geomorph", version = "3.0.6", repos = "http://cran.us.r-project.org")
#install.packages("http://https://cran.r-project.org/src/contrib/Archive/geomorph/geomorph_3.0.6.tar.gz", repos=NULL, type="source")
library(geomorph) # geomorph 3.0.6

#install_version("shapes", version = "1.2.3", repos = "http://cran.rstudio.com/") #"http://cran.us.r-project.org")
library(shapes) # shapes 1.2.3

@@

# The results are significant, but they cannot be explained by site difference
#lances_ANOVA<-procD.allometry(shape ~ size, ~site, data=lances_geomorph,method="PredLine") # Optional right-hand formula for the inclusion of groups; "~site" can be removed to perform ANOVA on whole dataset

# lances_ANOVA<-procD.allometry(shape ~ size, data=lances_geomorph,method="PredLine") # As above, but with "~site" removed
#plot(lances_ANOVA)
#print(lances_ANOVA)

@@

# plot the grid
ggpairs(lances_M, columns = c("total_length", "blade_length", "socket_length", "sock_bdiam", "sock_sdiam", "width", "thickness"), 
        upper=list(continuous = "points", mapping = aes(color = site)),
        lower=list(continuous = "cor"))#,
        #ggsave(here("Images","replication_fig_8v1.png")))

@@

ggpairs(lances_M, columns = c("total_length", "blade_length", "socket_length", "socket_max", "socket_min", "width", "thickness"), 
        upper=list(continuous = "points", mapping = aes(color = site)),
        lower=list(continuous = "cor"))#,
        #ggsave(here("Images","replication_fig_8v2.png")))
